\documentclass[]{resume}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.3\textwidth} 
\vspace{-2em}
\begin{large}
	\headername{Alish Kanani}\\
\end{large}
Final Year (B.Tech)\\
Electrical  Engineering\\ 
IIT Jodhpur  \\ 
\vspace{-1.8em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\vspace{-0.5em}
\noindent\rule{5.2cm}{0.4pt}\\

\vspace{-0.7em}
\runsubsection{B.Tech - Electrical Engineering}\\
IIT Jodhpur \\
Expected 2021\\
CGPA:8.9/10 (Till 6th Semester)\\

\vspace{-0.5em}
\runsubsection{Higher Secondary (HSC)}\\
Ashadeep Science Bhavan\\
2017 | Surat, Gujrat \\
Percentage: 94.4\%\\

\vspace{-0.5em}
\runsubsection{Secondary (SSC)}\\
M N J Patel High School\\
2015 | Surat, Gujrat \\
Percentage: 87.66\%\\
\sectionsep
\vspace{-1.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Relevant Courses}
\vspace{-0.5em}
\noindent\rule{5.2cm}{0.4pt}\\

\vspace{-0.7em}
\runsubsection{Electrical Core}\\
Digital Logic and Design\\
Microprocessors \& controllers\\
Analog Electronics\\
Signal and Power Integrity\\
Memory Architecture\\
Power Electronics\\
Circuit Theory\\
Communication Systems\\
Signals and Systems\\
Electrical Machine\\
Power System\\
Physics of Semiconductor Device\\
Digital Signal Processing\\
Control Systems\\

\vspace{-0.5em}
\runsubsection{Fundamental Mathematics}\\
Real Analysis and Linear Algebra\\
Complex Analysis and Differential Equations\\
Probability and Statistics\\
\sectionsep
\vspace{-1.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\vspace{-0.5em}
\noindent\rule{5.2cm}{0.4pt}

\vspace{0.5em}
\runsubsection{Languages}\\
C\\
Python (Basic)\\
MATLAB\\
Perl(Basic)\\

\vspace{-0.5em}
\runsubsection{HDL}\\
Verilog\\
HLS\\

\vspace{-0.5em}
\runsubsection{Softwares}\\
Vitis AI\\
ABC Synthesis Tool \\
Vitis (Basic) \\
Synopsys DC\\
Cadence Virtuoso(Basic)\\
Simulink\\

\vspace{-0.5em}
\runsubsection{Others}\\
Deep Neural Network(Basic)
LaTex\\
Arduino\\
\sectionsep
\end{minipage}
\hfill
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.69\textwidth} 
\hspace*{1pt}\hfill Mob. : +91 9664515665\\ 
\hspace*{1pt}\hfill Email. : \textbf{\href{mailto:kanani.1@iitj.ac.in}{\underline{kanani.1@iitj.ac.in}}}\\
\hspace*{1pt}\hfill Google Scholar : \textbf{\href{http://alishkanani.github.io}{\underline{Alish Kanani}}} \\
\hspace*{1pt}\hfill Github : \textbf{\href{https://github.com/AlishKanani}{\underline{github.com/AlishKanani}}}\\
\hspace*{1pt}\hfill LinkedIn : {\href{https://www.linkedin.com/in/alishkanani}{\underline{www.linkedin.com/in/alishkanani}}} \\
\vspace{-2.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Publications}
\vspace{-0.5em}
\noindent\rule{13cm}{0.4pt}
\vspace{-0.7em}
\runsubsection{}
\begin{itemize}
    \item Alish Kanani, Jigar Mehta, Neeraj Goel "\custombold{ACA-CSU: A Carry Selection Based Accuracy Configurable Approximate Adder Design}", IEEE Computer Society Annual Symposium on VLSI (ISVLSI), Limassol, Cyprus, 2020, pp. 434-439. {\href{https://doi.org/10.1109/ISVLSI49217.2020.00085}{\underline{\custombold{Paper}}}}\\
    \vspace{-2.6em}\\
    \item Rajat Bhattacharjya, Alish Kanani, Neeraj Goel "\custombold{ReARM: A Reconfigurable Approximate Rounding-Based Multiplier for Image Processing}", VLSI Design and Test 24rd International Symposium (VDAT), Bhubaneswar, India, 2020.\\
\end{itemize}
\sectionsep
\vspace{-2.7em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Internships
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Internships}
\vspace{-0.5em}
\noindent\rule{13cm}{0.4pt}

\vspace{0.2em}
\hspace{0.5em}
\runsubsection{FPGA Implementation of CRAFT Algorithm | TCS Research \& Innovation}\\
\hspace*{0.5em} Research Intern | May 2020 - Aug 2020 \\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Suggested implementation methods to speedup \href{https://arxiv.org/abs/1904.01941}{\underline{CRAFT}} text detection network on \href{https://www.xilinx.com/products/boards-and-kits/alveo.html}{\underline{Alveo}} FPGA. 
    \vspace{-0.6em}\\
    \item Learned \custombold{Vitis AI} and \custombold{HLS} for different kind of speedup technique. 
\end{itemize}
\sectionsep

\vspace{-0.8em}
\hspace{0.5em}
\runsubsection{Approximate 8bit Parallel Prefix Adder | TU Wien}\\
\hspace*{0.5em} Research Intern | May 2020-July 2020 | Guide:\href{mailto: Muhammad.shafique@tuwien.ac.at}{\underline{Prof. Muhammad Shafique}} \\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Proposed \custombold{1.4 Million} approximate adders from 4 different Prefix tree.
    \vspace{-0.6em}
    \item Automated process to extract performance and error matrix for each configuration using \custombold{ABC synthesis tool} and \custombold{python}.
\end{itemize}
\sectionsep

\vspace{-0.8em}
\hspace{0.5em}
\runsubsection{Accuracy Configurable Arithmetic Circuit | IIT Ropar}\\
\hspace*{0.7em}Research Intern | May 2019 - July 2019 | Guide: \href{mailto: neeraj@iitrpr.ac.in }{\underline{Dr Neeraj Goel}}\\
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Proposed Accuracy Configurable Adder and Multiplier
    \vspace{-0.6em}\\
    \item Compared proposed algorithms with state of the art algorithms using \custombold{Synopsys Design Compiler} and \custombold{octave}.
\end{itemize}
\sectionsep
\vspace{-1.7em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\vspace{-0.5em}
\noindent\rule{13cm}{0.4pt}

\vspace{0.2em}
\hspace{0.5em}
\runsubsection{DHVANIK - Wearable Tympanometric Diagnostic Tool for Middle Ear \hspace*{0.7em}Ailments}\\
\hspace*{0.5em} Inter IIT Project | Sep 2019 - Dec 2019 | Guide: \href{mailto: arpitkhandelwal@iitj.ac.in }{\underline{Dr Arpit Khandelwal}}\\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Developed a low-cost, user-friendly, IoT enabled, head-phone sized \custombold{tympanometer} that detects middle ear problem.
    \vspace{-0.6em}\\
    \item Made business model for IICDC 2019 and Inter IIT 2019.
\end{itemize}
\sectionsep

\vspace{-0.8em}
\hspace{0.5em}
\runsubsection{Optimisation of 32 bit adders | {\href{https://github.com/AlishKanani/32bitAdders}{\underline{\textcolor{black}{Code and Project Report}}}}}\\
\hspace*{0.5em} B.Tech Project | Jan 2019 - Apr 2019 | Guide: Dr S. P. Tiwari\\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Studied six different algorithms to add two binary numbers 
    \vspace{-0.6em}\\
    \item Compared delay, area and power of these algorithms in \custombold{Xilinx-ise}
\end{itemize}
\sectionsep

\vspace{-0.8em}
\hspace{0.5em}
\runsubsection{AES Data Encryption on FPGA | {\href{https://github.com/AlishKanani/AES}{\underline{\textcolor{black}{Code}}}}}\\
\hspace*{0.5em} Gymkhana Project | Sep 2018 - May 2019   \\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item developed an FPGA based encryption-decryption engine to facilitate speed up AES encryption.
\end{itemize}
\sectionsep

\vspace{-0.8em}
\hspace{0.5em}
\runsubsection{NETRA- Indoor Navigator for Visually Impaired}\\
\hspace*{0.7em}Texas Instruments IICDC Competition | Aug 2018 - May 2019\\ 
\vspace{-2em}
\descript{}
\begin{itemize}
    \item Applied dead reckoning for indoor navigation and implemented on \custombold{Beaglebone black} using 9 axis \custombold{IMU}
    \vspace{-0.6em}\\
    \item Audio and haptic feedback for navigation for the visually impaired.
\end{itemize}
\sectionsep
\vspace{-1.8em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     POR
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positions of Responsibility}
\vspace{-0.5em}
\noindent\rule{13cm}{0.4pt}

\custombold{Captain}| Electronics Club  | Aug 2018 - May 2019\\
\custombold{Student Guide} | Counselling Service | Aug 2018 - May 2019\\
\vspace{-0.7em}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Achievements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements}
\vspace{-0.5em}
\noindent\rule{13cm}{0.4pt}

\vspace{-0.9em}
\begin{itemize}
  \item Presented a poster of DHVANIK on Industry Day, IIT Jodhpur.  
  \vspace{-0.6em}
  \item Secured \custombold{Bronze} medal in Inter IIT Techmeet 2019.
  \vspace{-0.6em}
  \item Led the team of project NETRA and DHVANIK which reached the \custombold{semi-finals} of \custombold{DST} and \custombold{Texas Instruments} IICDC 2018 and 2019.
  \vspace{-0.6em}
  \item Secured First Place in the Analog Designs - an online contest by \custombold{Texas Instruments University Program.}
%   \item Presented poster on Approximate Multiplication at Research Conclave, IIT Guwahati.
%   \item Cleared JEE advanced 2017 with All India Rank 5743 .
\end{itemize}

\end{minipage} 
\end{document}  \documentclass[]{article}